% Remerciements
%
%   Grâce aux remerciements, l'auteur attire l'attention du lecteur
% sur l'aide que certaines personnes lui ont apportée, sur leurs
% conseils ou sur toute autre forme de contribution lors de la
% réalisation de son mémoire. Le cas échéant, c'est dans cette section
% que le candidat doit témoigner sa reconnaissance à son directeur de
% recherche, aux organismes dispensateurs de subventions ou aux
% entreprises qui lui ont accordé des bourses ou des fonds de
% recherche.
\chapter*{ACKNOWLEDGEMENTS}\thispagestyle{headings}
\addcontentsline{toc}{compteur}{ACKNOWLEDGEMENTS}
%
I would like to thank all those who have supported me during my graduate studies. Specially to Professor Michel Dagenais, who gave me his support and advice for this research.
 
I acknowledge all my committee members: Professor Michel Gagnon and Professor Daniel Aloise to evaluate my research contribution.
 
 Also I would like to thank my colleagues at DORSAL laboratory, for their valuable comments on my development. They’ve helped making my path possible with their precious comments and considerations.
 
Special thanks for Gabriel A., my uncle Nacib Asseff, and Leticia R. for their tremendous support during my studies and help in the several challenges faced.
 
I also would like to praise the Ecole Polytechnique de Montreal and the department of Computer and Software Engineering for giving me the opportunity of studying and working here. 
 
 Last but not the least; I would like to acknowledge my mother, Maria Pereira de Assis, for her imperative support throughout my path. 
 
\begin{flushleft}
\textit{Venimus, Vidimus, Deus vicit}
\end{flushleft}
